Irt plot extra

### 2023-01-16 manuscript_v3.Rmd

Our results focus on the development of the LEBA inventory and its psychometric validation using a large scale online sample data (n=`r nrow(data)`).

@@

We conducted two rounds of large scale online survey between 17 May 2021 and 3 September 2021 to generate data from `r nrow(data)` participants with varied geographic locations (countries=`r nrow(num.countries)`; time-zone=`r nrow(numUTC)`). For a complete list of geographic locations, see **Supplementary Table 2**. Table 1 presents the survey participants' demographic characteristics. Only participants completing the full LEBA inventory were included. We used the data from first round for the exploratory factor analysis (EFA sample; n=`r nrow(EFA.data)`) and data from the second round was used in the confirmatory factor analysis (CFA sample; n=`r nrow(CFA.data)`). Participants in our survey were aged between `r min(desctable.data$slypos_demographics_age)` to `r max(desctable.data$slypos_demographics_age)` years, with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 2)` years of age [Overall: `r mean(desctable.data$slypos_demographics_age)`±`r sd(desctable.data$slypos_demographics_age)`; EFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`±`r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`; CFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`±`r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`]. In the entire sample, `r desc_tibble[4,2]` were male, `r desc_tibble[3,2]` were female, `r desc_tibble[5,2]` reported other sex, and `r desc_tibble[6,2]` reported a gender-variant identity. In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers. For their "Occupational Status", more than half of the overall sample (`r desc_tibble[9,2]`) reported that they currently work, whereas `r desc_tibble[10,2]` reported that they go to school, and `r desc_tibble[11,2]` responded that they do "Neither". With respect to the COVID-19 pandemic, we asked participants to indicate their occupational setting during the last four weeks: In the entire sample, `r desc_tibble[13,2]` of the participants indicated that they were in a home office/ home schooling setting, `r desc_tibble[14,2]` reported face-to-face work/schooling, `r desc_tibble[15,2]`  reported a combination of home- and face-to-face work/schooling, and `r desc_tibble[16,2]`  filled in the "Neither (no work or school, or on vacation)" response option.

@@

We observed that the response patterns of LEBA inventory for the entire sample (n=`r nrow(sem.data)`) were not normally distributed (Figures \@ref(fig:efagtPic1) and \@ref(fig:efagtPic2)). All items violated both univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality [(@mardiaMeasuresMultivariateSkewness1970]. The multivariate skewness was`r printnum(mardia.all.data$b1p)` (p<0.001) and the multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p<0.001).

@@

Similar non-normal distribution of response pattern was also observed in the EFA sample. **Supplementary Figure 1** depicts the univariate descriptive statistics for the EFA sample (n=`r nrow(EFA.data)`). Further, We observed that each item's correlation with the aggregated sum of the 48-item's score varied largely (corrected item-total correlation= `r apa(low.r.corec,2,T)` -`r apa(high.r.corec,2,T)`) indicating the possibility of multi-factor structure  of the LEBA inventory.

@@

Exploratory analysis revealed that items of LEBA inventory can be categorized into five major factors: (i) wearing blue light filters; (ii) spending time out doors; (iii) using phone and smartwatch in bed; (iv) usinf light before bedtime (v) using light in the morning and during daytime. In this stage of analysis, we retained 25 items. the first factor had three items and encapsulated the individual's preference for using blue light filters in different light environments. The second factor contained six items that incorporated the individuals' hours spent outdoors. The third factor contained five items that looked into specific behaviours of using a phone and smartwatch in bed. The fourth factor comprised five items investigated the other behaviours related to the individual's electric light exposure before bedtime. lastly, the fifth factor encompassed six items capturing the individual's morning and daytime light exposure-related behaviour.

Prior to conducting the EFA, we have checked the post-hoc sampling adequacy by applying Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy on the EFA sample (n=`r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974] and the quality of the correlation matrix by Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954]. KMO>0.50 would indicate adequate sample size [@hutchesonMultivariateSocialScientist1999] and a significant test of sphericity would indicate satisfactory quality of the correlation matrix . Results indicated that we had an adequate sample size (KMO=`r printnum(KMO$MSA)`) and correlation matrix ($\chi^2_{1128}$=`r apa(bartlet$chisq, 2, T)`, p< 0.001). However, `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than |0.30|, and the inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`. Figure \@ref(fig:efa-plot-print)-A depicts the respective correlation matrix. To identify how many factors are required to optimally express human light exposure related behaviors we used a combination of methods. the Scree plot ( Figure \@ref(fig:efa-plot-print)-B) revealed a six-factor solution, whereas the minimum average partial (MAP) method [@velicerDeterminingNumberComponents1976] (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] implied a five-factor solution (Figure \@ref(fig:efa-plot-print)-C). Hence, we tested both five-factor and six-factor solutions using iterative EFA where we gradually identified and discarded problematic items (factor-loading <0.30 and cross-loading >0.30). In this process, we found a five-factor structure for LEBA inventory with 25 items. Table \@ref(tab:EFATable) displays the factor-loading ($\lambda$) and communality of the items. Both factor loadings and commonalities advocate to accept this five-factor solution ( |$\lambda$|= `r apa(min.loadings,2,T)` - `r apa(max.loadings, 2, T)`; commonalities= `r apa(min.com,2,T)` - `r apa(max.com, 2, T)`). These five factors explains `r apa(var1,2,T)`%, `r apa(var2,2,T)`%, `r apa(var3,2,T)`%, `r apa(var4,2,T)`%, `r apa(var5,2,T)`% of the total variance in individual's light exposure related behaviours respectively. All factors exhibited excellent to satisfactory reliability (ordinal $\alpha$= `r apa(F1.alpha,2,F)`, `r apa(F2.alpha,2,T)`, `r apa(F3.alpha,2,T)`, `r apa(F4.alpha,2,T)`, `r apa(F5.alpha,2,T)` respectively). The entire inventory also exhibited satisfactory reliability ($\omega_t$=`r apa(omega$omega.tot,2,T)`).

@@

To investigate the structural validity of the five-factor structure obtained in EFA, we conducted a confirmatory factor analysis (CFA) on the CFA sample. The five-factor structure with 25 items showed acceptable fit (Table \@ref(tab:tabCfa)) indicated that the five-factor structure fitted to the 25-item LEBA inventory attained an acceptable fit providing evidence of structural validity (CFI =`r apa(fit.1[5],2,T)`; TLI = `r apa(fit.1[6],2,T)`; RMSEA = `r apa(fit.1[7],2,T)` [`r apa(fit.1[8],2,T)`-`r apa(fit.1[9],2,T)`, 90% CI]). Two equity constraints were imposed on item pairs 32-33 (item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep) and 16-17 (item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day). Item pair 32-33 describes the preference for dimming the electric devices' brightness before bedtime, whereas item pair 16-17 represents the use of blue filtering or coloured glasses during the daytime. Given the similar nature of captured behaviours within each item pair, we accepted the imposed equity constraints. Nevertheless, the SRMR value exceeded the guideline recommendation (SRMR = `r apa(fit.1[10],2,T)`). In order to improve the model fit, we conducted a post-hoc model modification. Firstly, the  modification indices suggested cross-loadings between item 37 and 26 (item 37: I purposely leave a light on in my sleep environment while sleeping; item 26: I turn on my ceiling room light when it is light outside), which were hence discarded.  Secondly, items 30 and 41 (item 30: I look at my smartwatch within 1 hour before attempting to fall asleep; item 41: I look at my smartwatch when I wake up at night) showed a tendency to co-vary in their error variance (MI = 141.127, p<0.001 ). By allowing the latter pair of items (30 $\&$ 41) to co-vary, the model's error variance attained an improved fit (CFI =`r apa(fit.2[5],2,T)`; TLI = `r apa(fit.2[6],2,T)`); RMSEA = `r apa(fit.2[7],2,T)` [`r apa(fit.2[8],2,T)`-`r apa(fit.2[9],2,T)`, 90% CI]; SRMR = `r apa(fit.2[10],2,T) `).

Accordingly, we accept the five-factor model with 23 items, finalizing the long Form of LEBA inventory (see **Supplementary File 1**). Internal consistency ordinal $\alpha$ for the five factors of the LEBA were `r apa(rel.k[2,1],2,T)`, `r apa(rel.k[2,2],2,T)`, `r apa(rel.k[2,3],2,T)`, `r apa(rel.k[2,4],2,T)`, `r apa(rel.k[2,5],2,T)`, respectively. The reliability of the total inventory was satisfactory ($\omega_t$=`r apa(rel.k[5,6],2,T)`). Figure \@ref(fig:figcfa) depicts the obtained CFA structure, while  **Supplementary Figure 2** depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.

@@

We reported the measurement invariance (MI) analysis on the CFA sample based on native (n=`r mi.count[1,2]`) and non-native English speakers (n=`r mi.count[2,2]`). A detailed demographic description are provided in **Supplementary Table 5**.  Our MI results (Table \@ref(tab:InvarianceTab)) indicated that LEBA inventory demonstrated highest level of (residual model) psychometric equivalence across native and non-native English speaking participants, thus permitting group-mean based comparisons. The four fitted MI models generated acceptable fit indices and the model fit did not significantly decrease across the nested models ($\Delta$CFI>-0.01; $\Delta$RMSEA<0.01).

@@

```{r InvarianceTab, results='asis'}
apa_table(Invariance.table, align = "c",  caption = "Measurement Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; * =  df of model comparison.", landscape = T, font_size = "footnotesize", escape=F )

@@

## Secondary Analysis: Grade Level Identification and Semantic Scale Network Analysis
We investigated the language-based accessibility of LEBA using Flesch-Kincaid grade level analysis [@flesch1948new]. Results indicated that at least a language proficiency of educational grade level-four (US education system) with age above eight years  are requied to comprehend the items used in LEBA inventory. Semantic Scale analysis [@rosenbusch2020semantic]  was administered to assess the LEBA's (23 items) semantic relation to other questionnaires. LEBA inventory was most strongly semantically related to scales about sleep: The "Sleep Disturbance Scale For Children" [@bruni1996sleep] and the "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite]. The cosine similarity index ranged between .47 to .51.

@@

## Developing a Short Form of LEBA: IRT-Based Analysis
In order to derive a short form of the LEBA inventory, we fitted each factor of the LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=690). The resulting item discrimination parameters of the inventory fell into categories of "very high" (10 items), "high" (4 items), "moderate" (4 items), and "low" ( 5 items), indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**). An examination of the item information curve (**Supplementary Figure 3**) revealed five items (1, 25, 30, 38, & 41) provided very low information regarding light exposure related behaviors with relatively flat curves (I($\theta$) \<.20). We discarded those items, culminating in a short form of LEBA with five factors and 18 items (**Supplementary File 2**).

@@

```{r IRTparameters, eval=FALSE, include=FALSE, results='asis'}
apa_table(itemparameters, caption = "Items discrimination and response category difficulty thresholds of 23 items in  LEBA (n=690)", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
```

@@

Finally, **Supplementary Table 7** summarises the item fit indexes of the LEBA short form. All 18 items yielded RMSEA value $\le$0.06, indicating an adequate fit to the fitted IRT model. Furthermore, **Supplementary Figure 4** depicts the person fit Zh statistics histogram for the five IRT models. Zh statistics are larger than -2 for most participants, suggesting a good person fit regarding the selected IRT models.

```{r itemfittab, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='asis'}
apa_table(IRT.details , caption ="Item discrimination, response category difficulty thrsholds and fit statistics of the 18 items in short LEBA (n=690)",note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
```

@@

Data collected in the first round was used to explore the latent structure (EFA sample; n=`r nrow(EFA.descriptives)`). The exploratory factor analysis revealed a highly interpretable five-factor solution ("Wearing blue light filters", "Spending time outdoors", "Using phone and smartwatch in bed", "Using light before bedtime", and "Using light in the morning and during daytime") with 25 items. Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five-factor structure we obtained in our EFA, thus providing evidence for structural validity.(CFI=`r apa(fit.2[5],2,T)`; TLI=`r apa(fit.2[6],2,T)`; RMSEA=`r apa(fit.2[7],2,T)`). In this model, we discarded two more items (item 26 $\&$ 37 ) for possible cross-loadings. As a rule of thumb, reliability coefficients higher than .70 are regarded as “satisfactory”. However, at the early developmental stage, a value of .50 is considered acceptable [@dall2010developmental; @field2013discovering; @Nunnally1978]. Thus, we confer, the internal consistency coefficients ordinal alpha for the five factors and the total inventory were satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$=`r apa(rel.k[5,6],2,T)`).

@@

Often psychological measurements require application of several questionnaires simultaneously. Responding to several lengthy questionnaires increases the participants losing focus and becoming tried. To avoid these situations we  derived a short version of the LEBA (18 items) using IRT analysis. We fitted a graded response model to the combined EFA and CFA sample (n=`r nrow(data)`) and discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20]. The resulting test information curves suggest that the short-LEBA is a psychometrically sound measure with adequate coverage of underlying traits and can be applied to capture the frequency of different light exposure related behaviours reliably.

@@

We collected the survey data between 17 May 2021 and 3 September 2021 – firstly from `r nrow(EFA.descriptives)` participants (EFA sample) – and subsequently, another dataset from `r nrow(CFA.descriptives)` participants (CFA sample), totalling `r nrow(desctable.data)`.

>>>>

Our results focus on the development of the LEBA inventory and its psychometric validation using a large scale online sample data (n = `r nrow(data)`).

@@

We conducted two rounds of large scale online survey between 17 May 2021 and 3 September 2021 to generate data from `r nrow(data)` participants with varied geographic locations (countries = `r nrow(num.countries)`; time-zone = `r nrow(numUTC)`). For a complete list of geographic locations, see **Supplementary Table 2**. Table 1 presents the survey participants' demographic characteristics. Only participants completing the full LEBA inventory were included. We used the data from first round for the exploratory factor analysis (EFA sample; n = `r nrow(EFA.data)`) and data from the second round was used in the confirmatory factor analysis (CFA sample; n = `r nrow(CFA.data)`). Participants in our survey were aged between `r min(desctable.data$slypos_demographics_age)` to `r max(desctable.data$slypos_demographics_age)` years, with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 2)` years of age [Overall: `r mean(desctable.data$slypos_demographics_age)`±`r sd(desctable.data$slypos_demographics_age)`; EFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`±`r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`; CFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`±`r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`]. In the entire sample, `r desc_tibble[4,2]` were male, `r desc_tibble[3,2]` were female, `r desc_tibble[5,2]` reported other sex, and `r desc_tibble[6,2]` reported a gender-variant identity. In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers. For their "Occupational Status", more than half of the overall sample (`r desc_tibble[9,2]`) reported that they currently work, whereas `r desc_tibble[10,2]` reported that they go to school, and `r desc_tibble[11,2]` responded that they do "Neither". With respect to the COVID-19 pandemic, we asked participants to indicate their occupational setting during the last four weeks: In the entire sample, `r desc_tibble[13,2]` of the participants indicated that they were in a home office/ home schooling setting, `r desc_tibble[14,2]` reported face-to-face work/schooling, `r desc_tibble[15,2]`  reported a combination of home- and face-to-face work/schooling, and `r desc_tibble[16,2]`  filled in the "Neither (no work or school, or on vacation)" response option.

@@

We observed that the response patterns of LEBA inventory for the entire sample (n = `r nrow(sem.data)`) were not normally distributed (Figures \@ref(fig:efagtPic1) and \@ref(fig:efagtPic2)). All items violated both univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality [@mardiaMeasuresMultivariateSkewness1970]. The multivariate skewness was`r printnum(mardia.all.data$b1p)` (p<0.001) and the multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p<0.001).

@@

Similar non-normal distribution of response pattern was also observed in the EFA sample. **Supplementary Figure 1** depicts the univariate descriptive statistics for the EFA sample (n = `r nrow(EFA.data)`). Further, We observed that each item's correlation with the aggregated sum of the 48-item's score varied largely (corrected item-total correlation= `r apa(low.r.corec,2,T)` -`r apa(high.r.corec,2,T)`) indicating the possibility of multi-factor structure  of the LEBA inventory.

@@

Exploratory analysis revealed that items of LEBA inventory can be categorized into five major factors: (i) wearing blue light filters; (ii) spending time out doors; (iii) using phone and smartwatch in bed; (iv) using light before bedtime (v) using light in the morning and during daytime. In this stage of analysis, we retained 25 items. the first factor had three items and encapsulated the individual's preference for using blue light filters in different light environments. The second factor contained six items that incorporated the individuals' hours spent outdoors. The third factor contained five items that looked into specific behaviours of using a phone and smartwatch in bed. The fourth factor comprised five items investigated the other behaviours related to the individual's electric light exposure before bedtime. lastly, the fifth factor encompassed six items capturing the individual's morning and daytime light exposure-related behaviour.

Prior to conducting the EFA, we have checked the post-hoc sampling adequacy by applying Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy on the EFA sample (n = `r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974] and the quality of the correlation matrix by Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954]. KMO>0.50 would indicate adequate sample size [@hutchesonMultivariateSocialScientist1999] and a significant test of sphericity would indicate satisfactory quality of the correlation matrix . Results indicated that we had an adequate sample size (KMO = `r printnum(KMO$MSA)`) and correlation matrix ($\chi^2_{1128}$ = `r apa(bartlet$chisq, 2, T)`, p< 0.001). However, `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than |0.30|, and the inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`. Figure \@ref(fig:efa-plot-print)-A depicts the respective correlation matrix. To identify how many factors are required to optimally express human light exposure related behaviors we used a combination of methods. the Scree plot ( Figure \@ref(fig:efa-plot-print)-B) revealed a six-factor solution, whereas the minimum average partial (MAP) method [@velicerDeterminingNumberComponents1976] (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] implied a five-factor solution (Figure \@ref(fig:efa-plot-print)-C). Hence, we tested both five-factor and six-factor solutions using iterative EFA where we gradually identified and discarded problematic items (factor-loading <0.30 and cross-loading >0.30). In this process, we found a five-factor structure for LEBA inventory with 25 items. Table \@ref(tab:EFATable) displays the factor-loading ($\lambda$) and communality of the items. Both factor loadings and commonalities advocate to accept this five-factor solution ( |$\lambda$| = `r apa(min.loadings,2,T)`-`r apa(max.loadings, 2, T)`; commonalities = `r apa(min.com,2,T)`-`r apa(max.com, 2, T)`). These five factors explains `r apa(var1,2,T)`%, `r apa(var2,2,T)`%, `r apa(var3,2,T)`%, `r apa(var4,2,T)`%, `r apa(var5,2,T)`% of the total variance in individual's light exposure related behaviours respectively. All factors exhibited excellent to satisfactory reliability (ordinal $\alpha$ = `r apa(F1.alpha,2,T)`, `r apa(F2.alpha,2,T)`, `r apa(F3.alpha,2,T)`, `r apa(F4.alpha,2,T)`, `r apa(F5.alpha,2,T)` respectively). The entire inventory also exhibited satisfactory reliability ($\omega_t$=`r apa(omega$omega.tot,2,T)`).

@@

To investigate the structural validity of the five-factor structure obtained in EFA, we conducted a confirmatory factor analysis (CFA) on the CFA sample. The five-factor structure with 25 items showed acceptable fit (Table \@ref(tab:tabCfa)) providing evidence of structural validity (CFI = `r apa(fit.1[5],2,T)`; TLI = `r apa(fit.1[6],2,T)`; RMSEA = `r apa(fit.1[7],2,T)` [`r apa(fit.1[8],2,T)`-`r apa(fit.1[9],2,T)`, 90% CI]). Two equity constraints were imposed on item pairs 32-33 (item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep) and 16-17 (item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day). Item pair 32-33 describes the preference for dimming the electric devices' brightness before bedtime, whereas item pair 16-17 represents the use of blue filtering or coloured glasses during the daytime. Given the similar nature of captured behaviours within each item pair, we accepted the imposed equity constraints. Nevertheless, the SRMR value exceeded the guideline recommendation (SRMR = `r apa(fit.1[10],2,T)`). In order to improve the model fit, we conducted a post-hoc model modification. Firstly, the  modification indices suggested cross-loadings between item 37 and 26 (item 37: I purposely leave a light on in my sleep environment while sleeping; item 26: I turn on my ceiling room light when it is light outside), which were hence discarded.  Secondly, items 30 and 41 (item 30: I look at my smartwatch within 1 hour before attempting to fall asleep; item 41: I look at my smartwatch when I wake up at night) showed a tendency to co-vary in their error variance (MI = 141.127, p<0.001 ). By allowing the latter pair of items (30 $\&$ 41) to co-vary, the model's error variance attained an improved fit (CFI = `r apa(fit.2[5],2,T)`; TLI = `r apa(fit.2[6],2,T)`); RMSEA = `r apa(fit.2[7],2,T)` [`r apa(fit.2[8],2,T)`-`r apa(fit.2[9],2,T)`, 90% CI]; SRMR = `r apa(fit.2[10],2,T) `).

Accordingly, we accept the five-factor model with 23 items, finalizing the long Form of LEBA inventory (see **Supplementary File 1**). Internal consistency ordinal $\alpha$ for the five factors of the LEBA were `r apa(rel.k[2,1],2,T)`, `r apa(rel.k[2,2],2,T)`, `r apa(rel.k[2,3],2,T)`, `r apa(rel.k[2,4],2,T)`, `r apa(rel.k[2,5],2,T)`, respectively. The reliability of the total inventory was satisfactory ($\omega_t$ = `r apa(rel.k[5,6],2,T)`). Figure \@ref(fig:figcfa) depicts the obtained CFA structure, while  **Supplementary Figure 2** depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.

@@

We reported the measurement invariance (MI) analysis on the CFA sample based on native (n = `r mi.count[1,2]`) and non-native English speakers (n = `r mi.count[2,2]`). A detailed demographic description are provided in **Supplementary Table 5**.  Our MI results (Table \@ref(tab:InvarianceTab)) indicated that LEBA inventory demonstrated highest level of (residual model) psychometric equivalence across native and non-native English speaking participants, thus permitting group-mean based comparisons. The four fitted MI models generated acceptable fit indices and the model fit did not significantly decrease across the nested models ($\Delta$CFI>-0.01; $\Delta$RMSEA<0.01).

@@

```{r InvarianceTab, results='asis'}
apa_table(Invariance.table, align = "c",  caption = "Measurement Invariance analysis on CFA sample (n = 262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; * =  df of model comparison.", landscape = T, font_size = "footnotesize", escape=F )

@@

## Secondary Analysis: Grade Level Identification and Semantic Scale Network Analysis

We investigated the language-based accessibility of LEBA using Flesch-Kincaid grade level analysis [@flesch1948new]. Results indicated that at least a language proficiency of educational grade level-four (US education system) with age above eight years  are required to comprehend the items used in LEBA inventory. Semantic Scale analysis [@rosenbusch2020semantic]  was administered to assess the LEBA's (23 items) semantic relation to other questionnaires. LEBA inventory was most strongly semantically related to scales about sleep: The "Sleep Disturbance Scale For Children" [@bruni1996sleep] and the "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite]. The cosine similarity index ranged between 0.47 to 0.51.

@@

## Developing a Short Form of LEBA: IRT-Based Analysis

In order to derive a short form of the LEBA inventory, we fitted each factor of the LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=690). The resulting item discrimination parameters of the inventory fell into categories of "very high" (10 items), "high" (4 items), "moderate" (4 items), and "low" ( 5 items), indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**). An examination of the item information curve (**Supplementary Figure 3**) revealed five items (1, 25, 30, 38, & 41) provided very low information regarding light exposure related behaviors with relatively flat curves (I($\theta$) \<0.20). We discarded those items, culminating in a short form of LEBA with five factors and 18 items (**Supplementary File 2**).

@@

```{r IRTparameters, eval=FALSE, include=FALSE, results='asis'}
apa_table(itemparameters, caption = "Items discrimination and response category difficulty thresholds of 23 items in  LEBA (n = 690)", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
```

@@

Finally, **Supplementary Table 7** summarises the item fit indexes of the LEBA short form. All 18 items yielded RMSEA value $\le$ 0.06, indicating an adequate fit to the fitted IRT model. Furthermore, **Supplementary Figure 4** depicts the person fit Zh statistics histogram for the five IRT models. Zh statistics are larger than -2 for most participants, suggesting a good person fit regarding the selected IRT models.

```{r itemfittab, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='asis'}
apa_table(IRT.details , caption ="Item discrimination, response category difficulty thrsholds and fit statistics of the 18 items in short LEBA (n = 690)",note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
```

@@

Data collected in the first round was used to explore the latent structure (EFA sample; n=`r nrow(EFA.descriptives)`). The exploratory factor analysis revealed a highly interpretable five-factor solution ("Wearing blue light filters", "Spending time outdoors", "Using phone and smartwatch in bed", "Using light before bedtime", and "Using light in the morning and during daytime") with 25 items. Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five-factor structure we obtained in our EFA, thus providing evidence for structural validity.(CFI = `r apa(fit.2[5],2,T)`; TLI = `r apa(fit.2[6],2,T)`; RMSEA = `r apa(fit.2[7],2,T)`). In this model, we discarded two more items (item 26 $\&$ 37 ) for possible cross-loadings. As a rule of thumb, reliability coefficients higher than .70 are regarded as “satisfactory”. However, at the early developmental stage, a value of .50 is considered acceptable [@dall2010developmental; @field2013discovering; @Nunnally1978]. Thus, we confer, the internal consistency coefficients ordinal alpha for the five factors and the total inventory were satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$ = `r apa(rel.k[5,6],2,T)`).

@@

Often psychological measurements require application of several questionnaires simultaneously. Responding to several lengthy questionnaires increases the participants losing focus and becoming tried. To avoid these situations we  derived a short version of the LEBA (18 items) using IRT analysis. We fitted a graded response model to the combined EFA and CFA sample (n = `r nrow(data)`) and discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20]. The resulting test information curves suggest that the short-LEBA is a psychometrically sound measure with adequate coverage of underlying traits and can be applied to capture the frequency of different light exposure related behaviours reliably.

@@
